---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
library(classdata)
head(ames)
```
1. What variables are there?

There are 16 total variables for each house 

Parcel ID: House mailing number? unique 10 digit number 
Address: House address 
Style: Building style (1 Story Frame, 2 Story Frame, etc.)
Occupancy: Type of housing (Single-Family/Owner Occupied, Condominium, Townhouse, etc.)
Sale Date: Date the house was sold (date in yyyy-mm-dd)
Sale Price: Sale price of house ($)
Multi Sale: N/A or Y
YearBuilt: Year  of construction
Acres: Land
TotalLivingArea: House squarefootage (0-4000?)
Bedrooms: (NA - 8)
FinishedBsmtArea: Extra sqft if basement finished (NA - 2000)
LotArea: sqft of lot (NA - 200000)
AC: House air conditioned (Yes / No)
Fireplace: (Y / N)
Neighborhood: House location

2. Is there a variable of special interest?
Yes, "Sale Price"

3. Sale Price Exploration

Range: 0 - 20,500,000

```{r}
summary(ames$ 'Sale Price')
library(ggplot2)
ggplot(ames, aes(x = `Sale Price`)) + 
  geom_histogram(binwidth = 100000, color = "white", fill = "blue") + 
  labs(title = "House Sale Prices in Ames",
       x = "Sale Price ($)",
       y = "Number of times")
```
The histogram is heavily right skewed with many extreme outliers.

4. Acres (Will):
```{r}
summary(ames$ 'Acres')
library(ggplot2)
ggplot(ames, aes(x = `Acres`)) + 
  geom_histogram(binwidth = .05, color = "white", fill = "blue") + 
  labs(title = "Acre lot size in Ames",
       x = "Acres",
       y = "Number")
```
The pattern for the histogram is right skewed with some extreme outliers. This pattern is very similar to the main variable Sale Price in its right skew shape.

```{r}
ggplot(ames, aes(x = Acres, y = `Sale Price`)) +
  geom_point(alpha = 0.3)  + xlim(0, 5) + ylim(0, 1000000) +
  labs(title = "Relationship Between Lot Size and Sale Price",
       x = "Acres",
       y = "Sale Price ($)")
```
On this graph I noticed, similar to the histograms, a large density of points in the bottom left around the origin. This is a weak-positive relationship with many outliers. It seems that generally higher priced homes have more acreage, but some oddities are the houses with high acreage but low price and vice-versa.

4.TotalLivingArea (Blake)

```{r}
summary(ames$ 'TotalLivingArea (sf)')
library(ggplot2)
ggplot(ames, aes(x = `TotalLivingArea (sf)`)) + 
  geom_histogram(binwidth = 500, color = "white", fill = "blue") + 
  labs(title = "House Living Area Ames",
       x = "Living Area (sqft)",
       y = "Number of homes")
```
Range: 0-6007
The data is very slightly right skewed 

```{r}
ggplot(ames, aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) +
  geom_point(alpha = 0.3, color = "blue") + xlim(1, 6000) + ylim(1, 2000000)
  labs(title = "Relationship: Living Area vs. Sale Price",
       x = "Living Area (sqft)",
       y = "Sale Price ($)")
```

There is a strong positive relationship between TotalLivingArea (sf) and Sale Price of the homes in Ames. There are many outliers in this data set so they had to be removed.

