---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
library(classdata)
head(ames)
```
1. What variables are there?

There are 16 total variables for each house 

Parcel ID: House mailing number? unique 10 digit number 
Address: House address 
Style: Building style (1 Story Frame, 2 Story Frame, etc.)
Occupancy: Type of housing (Single-Family/Owner Occupied, Condominium, Townhouse, etc.)
Sale Date: Date the house was sold (date in yyyy-mm-dd)
Sale Price: Sale price of house ($)
Multi Sale: N/A or Y
YearBuilt: Year  of construction
Acres: Land
TotalLivingArea: House squarefootage (0-4000?)
Bedrooms: (NA - 8)
FinishedBsmtArea: Extra sqft if basement finished (NA - 2000)
LotArea: sqft of lot (NA - 200000)
AC: House air conditioned (Yes / No)
Fireplace: (Y / N)
Neighborhood: House location

2. Is there a variable of special interest?
Yes, "Sale Price"












